---
title: "Social Survey 2010"
author: "Jada Early"
date: "Fall 2018"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(tidyvertse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Use the data from the 2010 general social survey to explore whether belief in continental drift (condrift), views on capitol punishment (cappun), and race (race) are independent of each other.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

```{r}
alldata <- read.csv(file="gss2010.csv", header=TRUE)
#names(alldata)
```


## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
barchartGC(~race+condrift, data=alldata, type = "percent") 
```

  About 22% of Blacks do not believe continental drift is real, about 10% of others do not believe continental drift is real, and about 8% of whites do not believe continental drift is real.  

```{r}
barchartGC(~race+cappun, data=alldata, type = "percent")
```

   About 45% of Blacks are in favor of Capital punishment, 55% of others are in favor, and 70% of whites are in favor of capital punishment.  
  
```{r}
barchartGC(~cappun+condrift, data=alldata, type = "percent")
```
  
  
    10% of those in favor of capital punishment believe continental drift is false and 65% who do not believe incapital punishment do believe continental drift is real.  
    

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
```{r}
 tab1 =xtabs(~race+condrift, data=alldata)
rowPerc(tab1)
colPerc(tab1)
```

  The results show 23% of Blacks believe continental drift is false, 9% of others believe continental drift is false, and 8% of whites believe it is false.  
  
```{r}
tab2 =xtabs(~race+cappun, data=alldata)
rowPerc(tab2)
colPerc(tab2)
```

  The results show that 46% of Blacks are in favor of capital punishment, 56% of others, and 72% of whites are also in favor.  
  
```{r}
tab3 =xtabs(~cappun+condrift, data=alldata)
rowPerc(tab3)
colPerc(tab3)
```
  
    The results show that 10% of those in favor of capital punishment believe contintental drift is false and 11% who oppose it believe it is false. 
## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
```{r}
chisqtestGC(tab1,graph=TRUE)
```

  We reject the null hypothesis because the p-value is too low.
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

  The data appeared to be related. It did not seem to be independent. 
